\section{Conclusion}
\label{sec:conclusion}

We introduced FreshState, a pipeline for constructing temporally-grounded
benchmarks for web search staleness and evaluating their impact on language model
outputs. FreshState records ground-truth change events---price updates, listing
expirations, version releases---on live web pages and uses them in a controlled
snippet-swap experiment to measure whether models propagate stale information.

A 14-day prospective deployment monitoring 1,628 URLs across rental listings and
open-source software produces 474 change-event seeds (68 apartment, 406 software).
The software domain exhibits ${\sim}17\%$ daily change rates, while apartment
listings show ${\sim}1\%$ price-change rates alongside ${\sim}23\%$ daily expiration
rates. In the snippet-swap evaluation, stale context causes models to echo
outdated values at a 100\% rate across all three models tested, demonstrating that index lag is
not merely an information-retrieval problem but a direct source of factual error
in RAG pipelines.

\paragraph{Limitations.}
The current deployment covers two domains and a single geographic market (San
Francisco Bay Area) for apartment listings. The snippet-swap experiment uses
synthetic snippets (template-generated) rather than cached search engine results,
which may understate the complexity of real retrieval contexts. The 14-day window
captures short-term dynamics but not seasonal or long-term trends. Additionally,
Craigslist listings are intentionally ephemeral by design, representing an extreme
case; a broader benchmark should include more stable listing platforms.

\paragraph{Future work.}
Three directions stand out. First, extending to additional domains (job listings,
financial data, e-commerce products) would test extractor generalization and
broaden applicability. Second, integrating FreshState's change events with a live
search engine index would enable direct measurement of index lag---the time between
a real-world change and the moment a search engine reflects it. Third, FreshState's
labeled change events could serve as training data for a freshness-aware re-ranking
model that deprioritizes results likely to have gone stale, or as a calibration
signal for RAG systems to hedge their answers on time-sensitive queries.

\paragraph{Reproducibility.}
The FreshState pipeline is implemented in Python and scheduled via macOS launchd
(or Unix cron). All extractors, candidate collectors, monitor scripts, and the
snippet-swap experiment code are released alongside this paper. The seed datasets
produced by the 14-day deployment are published as a static benchmark artifact,
enabling future work to compare retrieval systems on identical temporal ground truth.

\paragraph{Ethics statement.}
FreshState collects publicly accessible web pages at a rate designed to stay well
within the bounds of polite crawling (one request per URL per day, with 1-second
rate limiting between requests). No user data is collected. The benchmark does not
include personal information. GitHub release pages and Craigslist listings are
public by design.
